### 2013-10-27 src2/thesis.tex
update

This thesis applies embedded language methodology to data-parallel programming. An 
embedded language is implemented as a library in a host language, Haskell in this case. 
The embedded language approach is beneficial since we are not entirely sure how 
to program current and future highly parallel computers. Implementing embedded languages allows 
us more rapid prototyping of ideas. Other benefits of embedded languages often listed 
are: making use of the host language's type system for guaranteeing generating correctly typed 
target code, parser and libraries (to some extent) 
and to have the host language as a powerful macro language for your embedded language.

>>>>

This thesis applies embedded language methodology to data-parallel programming. An 
embedded language is implemented as a library in a host language, Haskell in this case. 
The embedded language approach is beneficial since we are not entirely sure how 
to program current and future highly parallel computers. Implementing embedded languages allows 
us more rapid prototyping of ideas. Other benefits of embedded languages often listed 
are include making use of the host language's type system for guaranteeing generating correctly typed 
target code. Already existing libraries in the host language (if they are general enough) 
can be used in the embedded language. The host language can also be used as a powerful macro 
language for your embedded language.
